\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-10-01 NAR_DRAFT.tex
new language in the results section

\bkmcomment{I think there is a reasonable wording here in terms of positive predictive value.
Think of the threshold as the posterior class probability above which we set all probabilities to 1, and below to zero?
Getting better below but I still need to think harder.}
In practice, variant calling is a decision problem, in which a threshold score must be selected above which a variant call is made.
The proper threshold is ideally a choice the user makes based on their particular needs, which often balance precision with recall.
\batcave provides posterior probabilities averaged not only across the whole range of possible probabilities, but in particular at higher probability ranges applicable in most situations.
For posterior probability thresholds between 60 and 90\%, \batcave exhibits substantially better average calibration than MuTect (Fig.~\ref{NAR-ppv_fig}\&\ref{NAR-ppv_wgs_fig}).
As a result, \batcave posterior probabilities provide a useful way to select tumor-specific thresholds. 
For any posterior probability above 70\%, MuTect has a false positive rate of roughly 8\%, whereas \batcave has a false positive rate that decreases as the posterior probability increases.
%The cost of MuTect's compression is recall, which is 3-5\% worse than \batcave at 95\% posterior probability, and 3-7\% worse at 90\%, depending on mutation profile concentration.
At any posterior probability threshold \batcave has recall better than MuTect.
%Figure~\ref{NAR-ppv_wgs_fig} shows results for 100X whole genomes, where the results are similar for precision.

>>>>

In practice, variant calling is a classification problem, in which a threshold score must be selected above which a variant call is made.
The proper threshold is ideally a choice the user makes based on their particular needs, which often balance precision with recall.
The posterior probability estimates provided by \batcave allow the user to select a tumor-specific threshold.
For posterior probability thresholds between 60 and 90\%, \batcave exhibits positive predictive values that are relatively close to the threshold (Fig.~\ref{NAR-ppv_fig}\&\ref{NAR-ppv_wgs_fig}).
In other words, selecting a minimum posterior probability creates a classifier with positive predictive value close to that threshold.
On the other hand, the posterior probabilities from MuTect provide a poor estimate of positive predictive value (Fig.~\ref{NAR-ppv_fig}\&\ref{NAR-ppv_wgs_fig}).
For any posterior probability above 70\%, MuTect has a false positive rate of roughly 8\%, whereas \batcave has a false positive rate that decreases as the posterior probability increases.
As a result, \batcave posterior probabilities provide a useful way to select tumor-specific thresholds. 
At any posterior probability threshold \batcave has recall better than MuTect.
%The cost of MuTect's compression is recall, which is 3-5\% worse than \batcave at 95\% posterior probability, and 3-7\% worse at 90\%, depending on mutation profile concentration.
%Figure~\ref{NAR-ppv_wgs_fig} shows results for 100X whole genomes, where the results are similar for precision.
